Type-Safe Modular Parsing

### 2017-06-15 SLE_17/sections/CaseStudy.tex
Spell check. Bibtex.

The right part of table \ref{tab:comparison} suggests that the difference of running time between
using Object Algebras and class is little, roughly 1\%.
The usage of longest match combinator slows the performance by 7\%. The main reason of slower
execution time may be the overall structure of the modular parsing approach, because we indeed have
more intermediate function calls and method overriding. However, it is worth mentioning that
because of the memoization technique of Packrat parsers, we are only constant times
slower, the algorithmic complexity is still the same.
Since the slowdown seems to be caused by extra method
dispatching, in future work we wish to investigate techniques such as 
partial evaluation or meta-programming to eliminate such cost. The
work by B{\'e}guet and Manohar~\cite{Beguet:2014} is an interesting starting point.

>>>>

The right part of Table \ref{tab:comparison} suggests that the difference of running time between
using Object Algebras and class is little, roughly 1\%.
The usage of longest match combinator slows the performance by 7\%. The main reason of slower
execution time may be the overall structure of the modular parsing approach, because we indeed have
more intermediate function calls and method overriding. However, it is worth mentioning that
because of the memoization technique of Packrat parsers, we are only constant times
slower, the algorithmic complexity is still the same.
Since the slowdown seems to be caused by extra method
dispatching, in future work we wish to investigate techniques such as 
partial evaluation or meta-programming to eliminate such cost. The
work by B{\'e}guet and Manohar~\cite{Beguet:2014} is an interesting starting point.
